\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

While for \ClaudeThreeFiveSonnet the overall performance increased (less than 1\%), they show a sloped decrease for \GPTFourO compared with the \llm without tools (\Cref{tab:performance_table}). 
If we study the results by each type of question, we observe an improvement for questions regarding electron count or point group questions.
On the other hand, the scores decreased question asking about the number of isomers or information contained in pictograms.
For the specific questions about converting IUPAC names to SMILES, the results decreased notably despite the specific tools that were prepared for those questions. 
By studying the reasoning path for these cases, we found an important error in this ReAct configuration resulting from a bad response format of the model that results in an error raised by the LangChain framework.
This show that these agent configurations need to be really optimized for the task, and it is not only about equipping the \gls{llm} with tools, but also it requires of engineering work to improve the results.

>>>>

While for \ClaudeThreeFiveSonnet the overall performance increased (by less than 1\%), we observe a decrease in performance for \GPTFourO compared with the \llm without tools (\Cref{tab:performance_table}). 
If we study the results by each type of question, we observe an improvement for questions regarding electron count or point group questions.
On the other hand, the scores decreased question asking about the number of isomers or information contained in pictograms.
For the specific questions about converting IUPAC names to SMILES, the results decreased notably despite the specific tools that were prepared for those questions. 
By studying the reasoning path for these cases, we found an important error in this ReAct configuration resulting from a bad response format of the model that results in an error raised by the LangChain framework.
This show that these agent configurations need to be really optimized for the task, and it is not only about equipping the \gls{llm} with tools, but also it requires of engineering work to improve the results.
